Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-08-07 alloscore_manuscript/manuscript.Rnw
typo in bisection fig

p10 <- p + geom_hline(aes(yintercept = 10)) +
  geom_hline(aes(yintercept = c(2,8)), linetype = 2) +
  geom_segment(data = iters10, aes(x=taus, xend = taus, y=0, yend = qtot), color = "red", alpha = .5) +
  scale_x_continuous(limits = c(.45,1), expand = c(0,0), 
                     breaks = c(.5,.6,.7,.8,0.865,.9,1),
                     labels = c("0.5","0.6",
                                "0.7","0.8", 
                                expression(italic(atop(" ", 1 - e^{-1} %~~% 0.865)), "0.9", "1"))) +
  scale_y_continuous(limits = c(0,12), breaks = c(0,2,5,8,10,15), expand = c(0,0), 
                     name = element_blank())

>>>>

p10 <- p + geom_hline(aes(yintercept = 10)) +
  geom_hline(aes(yintercept = c(2,8)), linetype = 2) +
  geom_segment(data = iters10, aes(x=taus, xend = taus, y=0, yend = qtot), color = "red", alpha = .5) +
  scale_x_continuous(limits = c(.45,1), expand = c(0,0), 
                     breaks = c(.5,.6,.7,.8,0.865,.9,1),
                     labels = c("0.5","0.6",
                                "0.7","0.8", 
                                expression(italic(atop(" ", 1 - e^{-2} %~~% 0.865)), "0.9", "1"))) +
  scale_y_continuous(limits = c(0,12), breaks = c(0,2,5,8,10,15), expand = c(0,0), 
                     name = element_blank())
